---
title: "Hypothesis Tests and Linear Regression"
author: "Daeshik Park"
output: html_document
---

```{css, echo=FALSE}
pre {max-height: 300px; overflow-y: auto;
  max-width: 900px; overflow-x: auto;} # global setting for output blocks
#pre[class] {max-height: 50px;
  #max-width: 100px;} # global setting for code blocks (not working)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.height = 4.5, fig.width = 6, dpi = 100, fig.align = "center")
library(tidyverse)
```

<br>

```{r, results='hide'}
airbnb <- read_csv("AB_NYC_2019.csv")
str(airbnb)
```

<br>

### Hypothesis Test for a Proportion

```{r 1-prop z-test}
sum(is.na(airbnb$neighbourhood_group))
table(airbnb$neighbourhood_group)/length(airbnb$neighbourhood_group)
```

Test at the 95% confidence level if the percentage of people staying in Brooklyn Airbnbs differs from 40%.

```{r}
x <- airbnb %>% filter(neighbourhood_group == "Brooklyn") %>% nrow()
n <- nrow(airbnb)
prop.test(x, n, p = 0.4, alternative = "two.sided", conf.level = 0.95)
```

<br>

### Hypothesis Test for Difference of Proportions

```{r}
sum(is.na(airbnb$room_type))
table(airbnb$room_type)/length(airbnb$room_type)
```

Test at the 95% confidence level if the proportion of entire homes/apartments available is more than the proportion of private rooms available.

```{r 2-prop z-test}
x1 <- airbnb %>% filter(room_type == "Entire home/apt") %>% nrow()
x2 <- airbnb %>% filter(room_type == "Private room") %>% nrow()
x <- c(x1, x2)
n <- c(nrow(airbnb), nrow(airbnb))
prop.test(x, n, alternative = "greater", conf.level = 0.95)
```

<br>

### Hypothesis Test for a Mean

```{r}
summary(airbnb$price)
```

Test at the 95% confidence level if the mean price per night of an Airbnb in NYC is more than $150.

```{r one sample t-test}
t.test(airbnb$price, mu = 150, alternative = "greater", conf.level = 0.95)
```

<br>

### Hypothesis Test for Difference of Means

Test at the 95% confidence level if Staten Island has a higher average price per night than Queens.

```{r two sample t-test}
Staten <- airbnb %>% filter(neighbourhood_group == "Staten Island")
Queens <- airbnb %>% filter(neighbourhood_group == "Queens")
t.test(Staten$price, Queens$price, alternative = "greater", conf.level = 0.95)
```

<br>

### Hypothesis Test for Equality of Means

```{r}
by_nbd_group <- group_by(airbnb, neighbourhood_group)
summarise(by_nbd_group, mean(price))
```

Test at the 95% confidence level if the mean prices per night of the five boroughs in NYC are not equal.

```{r ANOVA test}
results <- aov(airbnb$price ~ airbnb$neighbourhood_group)
summary(results)
results
```

**Conclusion:** $p$-value $< \alpha$, so reject $H_0$. There is enough evidence to show that there is a relationship between borough and price. However, we do not know what that relationship is! We do not know which average prices are different!

<br>

### Hypothesis Test for Association of Categorical Variables

```{r}
freq_dist <- table(airbnb$neighbourhood_group, airbnb$room_type)
round(prop.table(freq_dist) * 100, 0)
```

```{r}
chisq.test(freq_dist)

chi_result <- chisq.test(freq_dist)
summary(chi_result)
chi_result
```

**Conclusion:** $p$-value $< \alpha$, so reject $H_0$. There is enough evidence to show that borough and room type are associated.  
There are ways to analyze what the relationship may be.

```{r}
chi_result$residuals
```

```{r}
library(corrplot)
corrplot(chi_result$residuals, is.corr = FALSE) # A graphical display of a correlation matrix, confidence interval. Also visualize a general matrix by setting is.corr = FALSE.
```

<br>

### Linear Regression and Correlation

```{r, scatter plot for numeric variables}
data("mpg")
mpg_num <- select_if(mpg, is.numeric)
pairs(mpg_num, col = "blue")
```

Multi-plots of one variable over multi-variables

```{r, fig.height = 4.5, fig.width = 8, dpi = 100, fig.align = "center"}
mpg_num %>% gather(-cty, key = "var", value = "value") %>%
  ggplot(aes(x = value, y = cty)) +
  geom_point(color = "green") +
  geom_jitter(color = "green") +
  geom_smooth(method = "lm") +
  facet_wrap(~ var, scales = "free")
```

It looks like the variables cty and hwy are linearly related in a strong and a positive way. Let's investigate the linear regression model between cty and hwy.

```{r, linear regression}
linear_mod <- lm(hwy ~ cty, data = mpg)
summary(linear_mod)
```

```{r, equation of the linear model}
hwy_predicted <- function(cty) {
  hwy_predicted <- linear_mod$coefficients[2] * cty + linear_mod$coefficients[1]
  return(hwy_predicted) }
hwy_predicted(25)
```

```{r}
ggplot(data = mpg, mapping = aes(cty, linear_mod$residuals)) +
  geom_count(col = "green") +
  geom_abline(intercept = 0, slope = 0, col = "blue", linetype = "longdash", size = 1)
```

```{r, correlation}
cor(mpg$cty, mpg$hwy)
```
<br>

### *The End*